A meta-analysis of powdery mildew yield loss mitigation strategies in Australian mungbean

### 2021-03-10 03_Yield_MetaAnalysis.Rmd
More spellchecking

Inspect a histogram of when first sign occured in the crop
```{r hist_onset}
PM_dat_Y %>%
   ggplot(aes(x = as.integer(first_sign_days))) +
   geom_histogram(binwidth = 1) +
   geom_vline(xintercept = 42)
```

@@

Inspect a histogram of when first sign occured in the crop
```{r hist_pressure}
PM_dat_Y %>%
   ggplot(aes(x = PM_final_severity)) +
   geom_histogram(binwidth = 1) +
   geom_vline(xintercept = 8)
```

>>>>

Inspect a histogram of when first sign occurred in the crop
```{r hist_onset}
PM_dat_Y %>%
   ggplot(aes(x = as.integer(first_sign_days))) +
   geom_histogram(binwidth = 1) +
   geom_vline(xintercept = 42)
```

@@

Inspect a histogram of when first sign occurred in the crop
```{r hist_pressure}
PM_dat_Y %>%
   ggplot(aes(x = PM_final_severity)) +
   geom_histogram(binwidth = 1) +
   geom_vline(xintercept = 8)
```
